Title here

### 2020-08-13 paper/paper.Rmd
remove the commented text that are no longer necessary

<!-- Below are listed several issues in projection pursuit optimisation. Some are general optimisation problems, while others are more specific too PP optimisation.  -->

@@

<!-- - *Multivariate optimisation*: In projection pursuit, the decision variable includes all the entries in the projection matrix, which is high-dimensional. Researchers would be better off if they could understand the relative position of different projection matrix in the high-dimensional space. (multivariate optimisation) -->

@@

<!-- Computational considerations: -->

@@

<!-- - is `search_geodesic` widely known in the research community - doesn't seem to find paper introducing this except (Cook, 1995). Any tools available to  better understand its searching process? -->

@@

<!-- Below listed several features characterise the optimisation procedures needed in projection pursuit -->

<!-- - *Being able to handle non-differentiable PPI function*: The PPI function could be non-differentiable, thus derivative free methods are preferred.  -->

<!-- - *Being able to optimise with constraints*: The constraint comes from projection matrix being an orthonormal matrix.  -->

<!-- - *Being able to find both local and global maximum*: Although the primary interest is to find the global maximum, local maximum could also reveal structures in the data that are of our interest.  -->

@@

## Motivation
<!-- Visual diagnostics can be real-time or post-run. Real time diagnostic directly uses the data produced in the algorithm to produce visual representation and thus doesn't need to store the data.   This section focuses on the definition and production of post-run diagnostics and the next section discusses real-time diagnostics. -->

@@

<!-- For each level of iteration, we design two types of indices: *index per iteration: $j$* is fixed for each observations in one iteration and has an increment of one once a new iteration starts. *index within iteration: $l$* has an increment of one for each observation in an iteration and starts over from one once a new iteration starts. -->

<!-- In projection pursuit optimisation algorithms, there is one level of iteration and hence exists three iterators: `id` indices each observation by a unique number; `tries` is the index per iteration iterator that gets updated once a search-and-interpolate step is finished; and `loop` is the index within iteration iterator and starts over from one at the beginning of a new `tries`. We give the interpolating basis a different index $k$ for projection pursuit guided tour. It is similar in nature to $l$ but is specific for interpolating bases, which is usually not part of the optimisation. -->

@@

<!-- \begin{equation} -->
<!-- \left[ -->
<!-- \begin{array}{ccccccc} -->
<!-- \ast & \mathbf{A}_{1,1,\ast} & \mathbf{A}_{2, l_1 +1,\ast} & \cdots & \mathbf{A}_{J,\sum_{i = 1}^{J-1}l_i +1,\ast} & \mathbf{A}_{J+1,\sum_{i = 1}^{J}l_i +1 ,\ast} \\ -->
<!-- \ast & \mathbf{A}_{1,2,\ast} & \mathbf{A}_{2,l_1 +2,\ast} & \cdots & \mathbf{A}_{J,\sum_{i = 1}^{J-1}l_i +2,\ast} & \mathbf{A}_{J+1,\sum_{i = 1}^{J}l_i +2, \ast} \\ -->
<!-- \vdots & \vdots & \vdots & \ddots & \vdots &\vdots   \\ -->
<!-- \ast & \mathbf{A}_{1, l, \ast} & \mathbf{A}_{2, l_1 + l, \ast} & \cdots & \mathbf{A}_{J+1, \sum_{i = 1}^{J-1}l_i + l, \ast}  & \mathbf{A}_{J + 1, \sum_{i = 1}^{J}l_i + l, \ast}\\ -->
<!-- \vdots & \vdots & \vdots & \ddots & \vdots &\vdots   \\ -->
<!-- \ast & \mathbf{A}_{1, l_1-1, \ast} & \mathbf{A}_{2, l_1 + l_2-1, \ast} & \cdots & \mathbf{A}_{J, \sum_{i = 1}^{J-1}l_i -1, \ast} & \mathbf{A}_{J+1, \sum_{i = 1}^{J+1} l_i-1, \ast}\\ -->
<!-- \mathbf{A}_{0,\ast,\ast} & \mathbf{A}_{1, l_1, \ast} & \mathbf{A}_{2, l_1 + l_2, \ast} & \cdots & \mathbf{A}_{J, \sum_{i = 1}^{J}l_i , \ast} & \ast\\ -->
<!-- \hline -->
<!-- \ast &\mathbf{A}_{1, \ast, 1} & \mathbf{A}_{2, \ast, k_1 + 1} & \cdots &\mathbf{A}_{J, \ast,\sum_{i = 1}^{J-1}k_i + 1}  & \ast\\ -->
<!-- \ast &\mathbf{A}_{1, \ast, 2} & \mathbf{A}_{2, \ast, k_1 + 2} & \cdots &\mathbf{A}_{J, \ast, \sum_{i = 1}^{J-1}k_i +2}  & \ast \\ -->
<!-- \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\ -->
<!-- \ast &\mathbf{A}_{1, \ast, k} & \mathbf{A}_{2, \ast, k_1 + k} & \cdots &\mathbf{A}_{J, \ast, \sum_{i = 1}^{J-1}k_i +k}  & \ast \\ -->
<!-- \vdots & \vdots & \vdots & \ddots & \vdots   & \vdots \\ -->
<!-- \ast &\mathbf{A}_{1, \ast, k_1} & \mathbf{A}_{2, \ast, k_1 + k_2} & \cdots &\mathbf{A}_{J, \ast,\sum_{i = 1}^{J}k_i} & \ast \\ -->
<!-- \end{array} -->
<!-- \right] -->
<!-- = -->
<!-- \left[ -->
<!-- \begin{array}{c} -->
<!-- \vphantom{A^J_1}\text{candidate basis} \\ -->
<!-- \vphantom{A^J_2}\text{candidate basis} \\ -->
<!-- \vphantom{\vdots} \vdots \\ -->
<!-- \vphantom{A^J_2}\text{candidate basis} \\ -->
<!-- \vphantom{\vdots} \vdots \\ -->
<!-- \vphantom{A^J_2}\text{candidate basis} \\ -->
<!-- \vphantom{A^J}\text{current/target basis} \\ -->
<!-- \hline -->
<!-- \vphantom{\text{NULL}}\text{interpolation basis} \\ -->
<!-- \vphantom{\text{NULL}}\text{interpolation basis} \\ -->
<!-- \vphantom{\text{NULL}}\vdots \\ -->
<!-- \vphantom{\text{NULL}}\text{interpolation basis} \\ -->
<!-- \vphantom{\vdots} \vdots \\ -->
<!-- \vphantom{\text{NULL}}\text{interpolation basis} \\ -->
<!-- \end{array} -->
<!-- \right] -->
<!-- \label{eq:matrixA} -->
<!-- \end{equation} -->

<!-- An optimisation procedure can easily generate hundreds or thousands sampling points and the question becomes what are the points we want to explore... [the classification of searching or updating points goes here and people should be clear what part of the points goes to the plot - this is the data part not the plot part. ] -->

<!-- In tour, all the points recorded in the global object can be divided into two broad categories: searching points and interpolating points -->

<!-- The concept of grammar of graphic requires a dataset to be supplied in making a plot, thus a global object needs to be created in the iterative algorithm. The variables will be mapped into element of a graphic to explore and thus should contain all the parameters of interest. The next section shows how a global object is created in projection pursuit guided tour. -->

@@

<!-- `tries` has an increment of one once the generator is called (equivalently a new target basis is generated); `info` records the stage the basis is in. This would include the `interpolation` stage and the detailed stage in the optimisation i.e. `direction_search`, `best_direction_search`, `line_search`and `best_line_search` for geodesic searching (`search_geodesic`); `random_search` and `new_basis` for simulating annealing (`search_better`). `loop` is the counter used for the optimisation procedure and thus will be `NA` for interpolation steps. `id` creates a sequential order of the basis.  -->

<!--  Another examples is a 2D projection of the larger dataset with two informative variable (`x2` and `x7`) using search_better method. Notice in this example, the dimension of the bases becomes 6 by 2. -->

<!-- ```{r glb-obj-2, echo = TRUE} -->
<!-- holes_2d_better %>% head(5)  -->
<!-- ``` -->

@@

>>>>

@@

<!-- - *Multivariate optimisation*: In projection pursuit, the decision variable includes all the entries in the projection matrix, which is high-dimensional. Researchers would be better off if they could understand the relative position of different projection matrix in the high-dimensional space. -->

@@

@@

@@

@@

## Motivation

@@

@@

@@

@@

<!-- In tour, all the points recorded in the global object can be roughly divided into two broad categories: searching points and interpolating points -->
